Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-22 Arxiv/main.tex
update introduction

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in. The data privacy is the persistent

Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to  introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

@@

In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy. There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zhang2015differential} and \citet{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private: \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential}  \citet{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself. The third topic where our work focus on is still very new.

@@

The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data where multinomially distributed. The \emph{bias} is represented by parameter $\vtheta$ represents the vector of parameters of a categorically distributed random variable.  The prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the componentwise sum of vectors of reals.

>>>>

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their service, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue in all data analysis algorithms. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue(), They guranteed the privacy in specific data analysis algorithms.

Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to  introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

@@

In Bayesian Inference data analysis, some algorithms have been studied and mechanisms proposed corresponded to maintain their differential privacy. There are 3 main topics: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \citet{dimitrakakis2014robust}, \citet{zhang2016differential}, \citet{zheng2015differential} and \citet{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \citet{Zhang2017privbayes}, \citet{dimitrakakis2015differential},  \citet{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself. The third topic where our work focus on is still very new.

@@

The beta-binomial model can be immediately generalized to Dirichlet-multinomial, with underlying data multinomially distributed. The \emph{bias} is represented by parameter $\vtheta$, the vector of parameters of a categorically distributed random variable. The prior distribution over $\vtheta\in [0,1]^{k}$
is given by a Dirichelet distribution, $\dirichlet(\valpha)$, for $k\in\mathbb{N}$,
and $\valpha\in(\mathbb{R}^{+})^{k}$, with p.d.f:
\[
  \Pr(\vtheta)\equiv\frac{1}{\mbetaf(\valpha)}\cdot \displaystyle\prod_{i=1}^{k}{\theta_i^{\alpha_i-1}}
\]
where $\mbetaf(\cdot)$ is the generalized beta function.
The data $\dataobs$ will be a sequence of $n\in\mathbb{N}$ values
coming from a universe $\datauni$, such that $\mid\datauni \mid=k$.
The likelihood function will be:
\[
  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i},
\]
with $\Delta \alpha_i=\displaystyle\sum_{j=1}^{n}\iverson{x_j=a_i}$, where $\iverson{\cdot}$ represents Iverson bracket notation.
Denoting by $\Delta\valpha$ the vector $(\Delta\alpha_1,\dots \Delta\alpha_k)$ the posterior distribution over $\vtheta$ turns out to be
\[
  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha). 
\]
where $+$ denotes the componentwise sum of vectors of reals.
